Large and Infinitary Quotient Inductive-Inductive Types

### 2020-01-10 draft/paper.tex
list of related work

>>>>

Cartmell \cite{gat}. Displayed categories Ahrens \cite{displayedcats}.

Paolo paper \cite{gabe}. Finitary case \cite{kaposi2019constructing}.

Direct construction of concrete QIIT: Streicher
\cite{streicher2012semantics}, Brunerie \cite{brunerie}, Ambroise
\cite{induction-is-enough}.

Higher inductive types: HIT descriptions \cite{niels,hiit}, HITs in
cubical type theories\cite{cubicalhits,10.1145/3290314}, semantics for
subclasses of HITs
\cite{lumsdaineShulman,10.1145/3209108.3209130,nielsmsc,sojakova,moeneclaey}
Construction of example IITs without UIP: Jasper \cite{jasper}.
